---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Shiny Atlantis

## Development

1. Clone this repo in RStudio, New Project, Version Control, Git, "https://github.com/shanerichards/shinyrAtlantis.git"
2. Click Tools/Project Options/Build Tools/Generate documentation with roxygen - click all options ON. 
3. Click Build & Reload in the Build Tab (or hit Ctrl-SHIFT-Enter). 
4. Make edits, build/reload/test, commit. 
5. Etc. 



## Usage


Install the package (from Github). 

```{r,eval=FALSE}
if (packageVersion("devtools") < 1.6) {
  install.packages("devtools")
}
devtools::install_github("shanearichards/shinyrAtlantis ")
```

Load and attach the package. 

```{r}
library(shinyrAtlantis)
```

## Spatial Distributions "sh.dist"

Shiny application for generating spatial distributions with constant density (per unit area)


```{r,eval=FALSE}

library(shinyrAtlantis)
# ====================================================================
# code to choose the spatial data file (.bgm)

bgm.file <- system.file("extdata", "BanzareAtlantis.bgm", package = "shinyrAtlantis")

# ====================================================================
# code to collect the spatial data and view

map.object <- make.dist.object(bgm.file)
sh.dist(map.object)

```


## Shiny PRM Run `shprm.R`

```{r,eval=FALSE}
library(shinyrAtlantis)

def.all.file <- system.file("extdata", "paramdefns.csv", package = "shinyrAtlantis")
def.grp.file <- system.file("extdata", "grpTemplates.csv", package = "shinyrAtlantis")
bgm.file <- system.file("extdata", "BanzareAtlantis.bgm", package = "shinyrAtlantis")
grp.file <- system.file("extdata", "AntarcticGroups.csv", package = "shinyrAtlantis")
prm.file <- system.file("extdata", "SO90_biol.prm", package = "shinyrAtlantis")

## prior to packaging, the scope of these file names was a bit "global"
obj <- make.prm.object(bgm.file, grp.file, prm.file, def.all.file, def.grp.file)
## this def.grp.file contents should be included in object above??
sh.prm(obj, def.grp.file)  # run the shiny App

```


## Shiny INIT Run `shinit.R`

```{r,eval=FALSE}
library(shinyrAtlantis)


bgm.file <-system.file("extdata", "BanzareAtlantis.bgm", package = "shinyrAtlantis")

nc.file <- system.file("extdata", "input.nc", package = "shinyrAtlantis")

input.object <- make.init.object(bgm.file, nc.file)
a <- sh.init(input.object)
```


## One step launch

To launch any the above apps in one step, run the these examples.  


```{r,eval=FALSE}
shinyrAtlantis::SpatialDistributionsExample()
```

```{r,eval=FALSE}
shinyrAtlantis::DisplayParametersExample()
```

```{r,eval=FALSE}
shinyrAtlantis::DisplayInitializationExample()
```
