---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)

    # shiny,
    # dplyr,
    # DT,
    # ggplot2,
    # stringr,
    # vat,
    # scales
    # 
```

## Shiny Atlantis

## Development

1. Clone this repo in RStudio, New Project, Version Control, Git, "https://github.com/shanerichards/shinyrAtlantis.git"
2. Click Tools/Project Options/Build Tools/Generate documentation with roxygen - click all options ON. 
3. Click Build & Reload in the Build Tab (or hit Ctrl-SHIFT-Enter). 
4. Make edits, build/reload/test, commit. 
5. Etc. 



## Usage

Install these dependencies. 

```{r,eval=FALSE}

install.packages(c("DT", "dplyr", "ggplot2", "scales", "shiny", "stringr", "data.table"))
#devtools::install_github(repo = "mareframe/vat")
```

Install the package (from private Github). 

```{r,eval=FALSE}
install.packages("devtools")
devtools::install_git("shanearichards/shinyrAtlantis ")
```

Load packages (can fix by namespace later)

```{r}
library(shinyrAtlantis)
```

## Spatial Distributions "sh.dist"

Shiny application for generating spatial distributions with constant density (per unit area)


```{r,eval=FALSE}
library(shiny)
library(dplyr)
library(ggplot2)
library(DT)
library(stringr)

library(shinyrAtlantis)
# ====================================================================
# code to choose the spatial data file (.bgm)

bgm.file <- system.file("extdata", "BanzareAtlantis.bgm", package = "shinyrAtlantis")

# ====================================================================
# code to collect the spatial data and view

map.object <- make.dist.object(bgm.file)
sh.dist(map.object)

```


## Shiny PRM Run `shprm.R`

```{r,eval=FALSE}
library(shinyrAtlantis)


def.all.file <- system.file("extdata", "paramdefns.csv", package = "shinyrAtlantis")
def.grp.file <- system.file("extdata", "grpTemplates.csv", package = "shinyrAtlantis")
bgm.file <- system.file("extdata", "BanzareAtlantis.bgm", package = "shinyrAtlantis")
grp.file <- system.file("extdata", "AntarcticGroups.csv", package = "shinyrAtlantis")
prm.file <- system.file("extdata", "SO90_biol.prm", package = "shinyrAtlantis")

obj <- make.prm.object(bgm.file, grp.file, prm.file)
sh.prm(obj) # run the shiny App

```


## Shiny INIT Run `shinit.R`

```{r,eval=FALSE}
library(shinyrAtlantis)


bgm.file <-system.file("extdata", "BanzareAtlantis.bgm", package = "shinyrAtlantis")

nc.file <- system.file("extdata", "input.nc", package = "shinyrAtlantis")

input.object <- make.init.object(bgm.file, nc.file)
a <- sh.init(input.object)
```


## One step launch

To launch any the above apps in one step, run the these examples.  


```{r,eval=FALSE}
shinyrAtlantis::SpatialDistributionsExample()
```

```{r,eval=FALSE}
shinyrAtlantis::DisplayParametersExample()
```

```{r,eval=FALSE}
shinyrAtlantis::DisplayInitializationExample()
```
